Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System

### 2015-06-30 MUSES_vs_BYOD_solutions.tex
@pacastillo 's comments, abstract and section 2

One of the tasks of a CSO is to elaborate an efficient set of Information Security Policies (ISPs), for controlling a certain, and already known, structure \cite{Opp_Security11}. This means that, until the appearance of BYOD, enterprises used to follow static security policies devoted to control an environment where the company assets and the devices were purchased and maintained by the company. Now that corporate networks are becoming dynamic for being adapted to this BYOD philosophy, there is an additional risk as employees' devices are not always company-owned. This means that the CSOs have to find the balance between having a fast response to any user action that might cause harm (in terms of money loss because of a security incident), and trying not to intrude into users' privacy. %Pedro, me señalaste esto como para modificarlo por algo en plan "tratar de evitar intromisiones en la privacidad". ¿Te parece bien esto?
A needed security policy, or in this case, an ISP should deal with the way of protecting a certain organization's information against a security breach. Though there are standards, such as the ISO27002 or the Security Forum's Standard of Good Practice\footnote{\url{https://www.securityforum.org}}, and many guidelines \cite{SecPol09}, an ISP should be adapted depending on the characteristics of the community or organisation that they are built for. In this sense, MUSES stands up for a self-adaptation of the security policies of a company.

On the other hand, employee-owned devices like smartphones, can be both used for personal matters at work, and for continuing working outside of the workplace. As the name says, smartphones are more than simple mobile phones, and people who use them in their works have the possibility of maintaining a good balance between work and private life. For this reason, the risk of uncontrolled devices accessing to corporate assets in unsafe conditions, due to the number of new risks which are linked to smartphones \cite{gangula2013survey}, is bigger.

Normally, the enterprise network architecture was being adapted to cope with external attackers \cite{MIT05}. With the incorporation of BYOD, the threat is about corporate assets being compromised due to employees' devices with vulnerabilities \cite{android11}, or leaked because they are being accessed from a device connected through an insecure (public) network.

Thus now, more risky situations should be considered when designing a company's network architecture. In Figure \ref{fig:proposed_diagram} there is a proposal which can be used for the beginning of the study of solutions that may secure such a dynamic environment. It includes the possibility of having employee-owned mobile (smartphones and tablets) and portable (laptops) devices, and also the opportunity that the employees have of connecting these devices either from inside or outside the company premises. Moreover, company's information assets are constantly accessed under these conditions, considering that an information asset means every \textit{piece of information} that has a \textit{value} (cost depending on the risk of being lost or leaked) for the company. It can be referred to files with sensitive information, as well as confidential mails, or even to company applications.

>>>>

One of the tasks of a CSO is to elaborate an efficient set of Information Security Policies (ISPs), for controlling a certain, and already known, structure \cite{Opp_Security11}. This means that, until the appearance of BYOD, enterprises used to follow static security policies devoted to control an environment where the company assets and the devices were purchased and maintained by the company. Now that corporate networks are becoming dynamic for being adapted to this BYOD philosophy, there is an additional risk as employees' devices are not always company-owned. This means that the CSOs have to find the balance between having a fast response to any user action that might cause harm (in terms of money loss because of a security incident), and trying not to intrude into users' privacy. %Pedro, me señalaste esto como para modificarlo por algo en plan "tratar de evitar intromisiones en la privacidad". ¿Te parece bien esto?
A needed security policy, or in this case, an ISP should deal with the way of protecting a certain organization's information against a security breach. Though there are standards, such as the ISO27002 or the Security Forum's Standard of Good Practice\footnote{\url{https://www.securityforum.org}}, and many guidelines \cite{SecPol09}, an ISP should be adapted depending on the characteristics of the community or organisation that they are built for. In this sense, MUSES stands up for a self-adaptation of company security policies.

On the other hand, employee-owned devices like smartphones, can be both used for personal matters at work, and for continuing working outside of the workplace. Smartphones are more than simple mobile phones, and people who use them in their works have the possibility of maintaining a good balance between work and private life. For this reason, the risk of uncontrolled devices accessing to corporate assets in unsafe conditions, due to the number of new risks which are linked to smartphones \cite{gangula2013survey}, is increasing.

Usually, the enterprise network architecture is being adapted to cope with external attackers \cite{MIT05}. However, with the incorporation of BYOD, the threat is about corporate assets being compromised due to employees' devices with vulnerabilities \cite{android11}, or leaked because they are being accessed from a device connected through an insecure (public) network.

Thus now, more risky situations should be considered when designing a company's network architecture. Figure \ref{fig:proposed_diagram} shows the proposal that can be used to start the study of solutions that may secure such a dynamic environment. It includes the possibility of having employee-owned mobile (smartphones and tablets) and portable (laptops) devices, and also the opportunity that the employees have of connecting these devices either from inside or outside the company premises. Moreover, company's information assets are constantly accessed under these conditions, considering that an information asset means every \textit{piece of information} that has a \textit{value} (cost depending on the risk of being lost or leaked) for the company. It can be referred to files with sensitive information, as well as confidential mails, or even to company applications.
